Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-25 tex/paper1/paper1.tex
last of james' edits
plots in figures now have labels

%\documentclass[onecolumn]{emulateapj}
\documentclass[preprint]{aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
%\usepackage{showkeys}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{wasysym}
%\usepackage{subfigure}
\usepackage{verbatim}

@@

  {\bf The dynamics of regions of the solar corona are investigated
    using AIA 171\AA\ and 193\AA\ data.  The coronal emission from the
    quiet Sun, coronal loop footprints, coronal moss, and from above a
    sunspot is studied.  It is shown that the \mFpa\ in these regions
    can be described by a \PL\ at lower frequencies that tails to
    flat spectrum at higher frequencies, plus a Gaussian-shaped
    contribution that varies depending on the region studied. This
    Fourier spectral shape is in contrast to the commonly-held
    assumption that coronal time-series are well described by the sum
    of a long time-scale background trend plus Gaussian-distributed
    noise, with some specific locations also showing an oscillatory
    signal.  The implications of this discovery to the field of
    coronal seismology and the automated detections of oscillations
    are discussed.  The observed \PL\ shape of the Fourier power
    spectrum is interpreted as being due to the summation of a
    distribution of exponentially decaying emission events along the
    line of sight.}  This is consistent with the idea that the solar
  atmosphere is heated everywhere by small energy deposition events.
\end{abstract}

@@

\begin{figure}
\centerline{
\plottwo{loopfootpoints.centralpower.eps}{qs.centralpower.eps}
}
\centerline{
\plottwo{sunspot.centralpower.eps}{moss.centralpower.eps}
}
\caption{Log-log plot of the Fourier power of a time-series at the AIA
  pixel overlying a randomly chosen pixel in each of the regions
  considered (see Figure \protect\ref{fig:loc171193}).  The vertical
  black lines indicate the 3 and 5 minute frequencies.}
\label{fig:compare171193}
\end{figure}

>>>>

\documentclass[onecolumn]{emulateapj}
%\documentclass[preprint]{aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
%\usepackage{showkeys}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{wasysym}
%\usepackage{subfigure}
\usepackage{verbatim}

@@

  {\bf The dynamics of regions of the solar corona are investigated
    using AIA 171\AA\ and 193\AA\ data.  The coronal emission from the
    quiet Sun, coronal loop footprints, coronal moss, and from above a
    sunspot is studied.  It is shown that the \mFpa\ in these regions
    can be described by a \PL\ at lower frequencies that tails to flat
    spectrum at higher frequencies, plus a Gaussian-shaped
    contribution that varies depending on the region studied. This
    Fourier spectral shape is in contrast to the commonly-held
    assumption that coronal time-series are well described by the sum
    of a long time-scale background trend plus Gaussian-distributed
    noise, with some specific locations also showing an oscillatory
    signal.  The implications of this discovery to the field of
    coronal seismology and the automated detections of oscillations
    are discussed.  The \PL\ contribution to the shape of the Fourier
    power spectrum is interpreted as being due to the summation of a
    distribution of exponentially decaying emission events along the
    line of sight.}  This is consistent with the idea that the solar
  atmosphere is heated everywhere by small energy deposition events.
\end{abstract}

@@

\begin{figure}
\centerline{
\plottwo{loopfootpoints.centralpower.eps}{moss.centralpower.eps}
}
\centerline{
\plottwo{qs.centralpower.eps}{sunspot.centralpower.eps}
}
\caption{Log-log plot of the Fourier power of a time-series at the AIA
  pixel overlying a randomly chosen pixel in each of the regions
  considered (see Figure \protect\ref{fig:loc171193}).  The vertical
  black lines indicate the 3 and 5 minute frequencies.}
\label{fig:compare171193}
\end{figure}
